Cluster Analysis: Identifying Parkinson's Disease Subtypes

### 2015-06-25 writeup/parkinsons.tex
fix tex syntax error
Switch to using unscaled decision trees
These are more important for sensible interpretation
Add silhouette plots to writeup
Note - silhouette plots look good but continue to observe that the
average silhouette width (done by PAM, which should be comparable since
I can't find a lazy method for kmeans) is very weak, indicating little
structure?

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.8\linewidth]{dtree-kmeans-pruned-2.pdf}
  \caption{Decision Tree from $k$-means clustering, 2 clusters}
  \label{fig:kmeans-dtree-2}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.8\linewidth]{dtree-kmeans-pruned-3.pdf}
  \caption{Decision Tree from $k$-means clustering, 3 clusters}
  \label{fig:kmeans-dtree-3}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.8\linewidth]{dtree-kmeans-pruned-4.pdf}
  \caption{Decision Tree from $k$-means clustering, 4 clusters}
  \label{fig:kmeans-dtree-4}
\end{figure}

@@

\end{lstlisting}
\section{Biclustering}

>>>>

\subsection{Silhouette plots}

Available in
Figures~\ref{fig:kmeans-silhouette-2},~\ref{fig:kmeans-silhouette-3},
and~\ref{fig:kmeans-silhouette-4}. Note: constructed with standardized
$z$-score data.

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.8\linewidth]{kmeans-silhouette-2.pdf}
  \caption{$k$-means cluster silhouette plot, $k = 2$}
  \label{fig:kmeans-silhouette-2}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.8\linewidth]{kmeans-silhouette-3.pdf}
  \caption{$k$-means cluster silhouette plot, $k = 3$}
  \label{fig:kmeans-silhouette-3}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.8\linewidth]{kmeans-silhouette-4.pdf}
  \caption{$k$-means cluster silhouette plot, $k = 4$}
  \label{fig:kmeans-silhouette-4}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.8\linewidth]{dtree-kmeans-pruned-unscaled-2.pdf}
  \caption{Decision Tree from $k$-means clustering, 2 clusters}
  \label{fig:kmeans-dtree-2}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.8\linewidth]{dtree-kmeans-pruned-unscaled-3.pdf}
  \caption{Decision Tree from $k$-means clustering, 3 clusters}
  \label{fig:kmeans-dtree-3}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.8\linewidth]{dtree-kmeans-pruned-unscaled-4.pdf}
  \caption{Decision Tree from $k$-means clustering, 4 clusters}
  \label{fig:kmeans-dtree-4}
\end{figure}

@@

\section{Biclustering}
